\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-25 paper.tex
simulation setup finished

\subsection{Simulations}
\textbf{Simulation setup.} 
We also conduct simulations on four real network topologies, including B4 \cite{B4}, ATT \cite{Teavar}, IBM\cite{SMORE} and a national-level backbone. 
Table \ref{evaluation-topologies} shows the topology details
\footnote{For B4, ATT and IBM, we get their topologies, link capacities and traffic matrices from the authors of TEAVAR\cite{Teavar}, and for the national backbone, we conduct a direct measurement on it but hide its name due to anonymity requirement.}. 
Following the conclusion on WAN failures in literature studies\cite{Characterization, Teavar}, 
we simulate link failures according to a Weibull distribution with its shape $\lambda=0.8$ and scale $k=0.00001$. 
We generate the demand workload in a similar way to that in the testbed. 
The arrivals of BA demands follow a Poisson process, with a mean inter-arrival time of 2 minutes. 
The duration of each demand follows an exponential distribution, and the mean duration corresponds to 1000 time slots.
The required bandwidth in each user demand is randomly drawn from the traffic metrices (we have collected 200 matrices for each topology) with a proper scale down factor (we use 5), so that between each source-destination pair, multiple users can be served simultaneously. 
The required availability in each user demand is drawn from 10 different SLAs of Azure\cite{azure}.
In addition to FFC and TEAVAR, the TE algorithms we compare in simulations also include 
SWAN \cite{swan}, SMORE \cite{SMORE} and B4 \cite{B4}. 
We assume at most one link failure (i.e., no concurrent failures) in FFC,  
use 99.9\% (the maximum value in the user demands) as the default availability target in TEAVAR,
and let SWAN maximize the total throughput of all users. 
These TE algorithms will be activated every 10 time slots.
With the above settings, each simulation lasts 150,000 slots (corresponding to 100 days if each slot represents 1 minute), and the results that achieved by each algorithm on each topology are calculated on 5 independent simulations with different workload traces.

>>>>

\subsection{Simulations}
\textbf{Simulation setup.} 
We also conduct simulations on four real network topologies, including B4 \cite{B4}, ATT \cite{Teavar}, IBM\cite{SMORE} and a national-level backbone. 
Table \ref{evaluation-topologies} shows the topology details
\footnote{For B4, ATT and IBM, we get their topologies, link capacities and traffic matrices from the authors of TEAVAR\cite{Teavar}, and for the national backbone, we conduct a direct measurement on it but hide its name due to anonymity requirement.}. 
Following the conclusion on WAN failures in literature studies\cite{Characterization, Teavar}, 
we simulate link failures according to a Weibull distribution with its shape $\lambda=0.8$ and scale $k=0.00001$. 
We generate the demand workload in a similar way to that in the testbed. 
The arrivals of BA demands follow a Poisson process, with a mean inter-arrival time of 2 minutes. 
The duration of each demand follows an exponential distribution, and the mean duration corresponds to 1000 time slots.
The required bandwidth in each user demand is randomly drawn from the traffic metrices (we have collected 200 matrices for each topology) with a proper scale down factor (we use 5), so that between each source-destination pair, multiple users can be served simultaneously. 
The required availability in each user demand is drawn from 10 different SLAs of Azure\cite{azure}.
In our simulations, besides FFC and TEAVAR, we also compare against several other TE algorithms,  
including SWAN \cite{swan}, SMORE \cite{SMORE} and B4 \cite{B4}. 
They have not explicitly considered availability, but pay attention to 
total throughput, link utilization or user fairness. 
These TE algorithms will be activated every 10 time slots.
We assume at most one link failure (i.e., no concurrent failures) in FFC,  
use 99.9\% (the maximum value in the user demands) as the default availability target in TEAVAR,
and let SWAN maximize the total throughput of all users. 
With the above settings, each simulation lasts 150,000 slots (corresponding to 100 days if each slot represents 1 minute), and the results that achieved by each algorithm on each topology are calculated on 5 independent simulations with different workload traces.
